Cost of Living in Toronto

### 2024-09-27 paper/paper.qmd
fixed a typo in paper.qmd

data_long <- data %>%
  pivot_longer(cols = c(Income, Expenses), 
               names_to = "Type", 
               values_to = "Amount")

>>>>

# code idea acquired from https://stackoverflow.com/questions/10212106/creating-grouped-bar-plot-of-multi-column-data-in-r
data_long <- data %>%
  pivot_longer(cols = c(Income, Expenses), 
               names_to = "Type", 
               values_to = "Amount")
